A quantitative framework for investigating the reliability of empirical network construction

### 2018-11-23 manuscript/CI_interactions.tex
adding refs

    First and foremost, ecological communities are known to be stochastic~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilites and hence in interactions~\citep{Vazquez2005,Poisot2015,Graham2018}. Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013}. Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012,Emer2018}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}, throughout life cycles~\citep{Preston2014,Clegg2018}, and with environmental conditions~\citep{Poisot2015}.

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007,Jordano2016}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeeus2013,Poisot2016}. Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Williams2010,Rohr2016}. These models may be based on species traits and/or abundances~\citep{Rohr2016,Graham2018,more} or on simple abstract rules~\citep{Allesina2008,Williams2010}. Such networks provide an important ''reality check'' by allowing us to compare the observed network to what would be expected under a particular set of assumptions~\citep{Bartomeus2013,Weinstein??}. They allow us to estimate the numbers of interactions which have not been observed and predict which unobserved interactions are most likely~\citep{Bartomeus2013}. Alternatively, it is possible to estimate the number of unobserved interactions which likely occurred~\citep{Jordano2016}. This...

@@

      We start from the perspective of a community ecologist faced with the task of describing a previously unknown interaction network. This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.  Importantly, the information sought is conveyed by both the presence and \emph{absence} of links. Presences and absences are not, however, equally certain. An observed link definitely occurred, but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}. In terms of the ones and zeros in a binary interaction matrix, we know that the ones are true but we cannot be sure that the zeros reflect interactions which actually do not occur. The detection of any interaction is a stochastic process. As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty: interaction uncertainty, process uncertainty, and detection uncertainty (Fig.~\ref{conceptual_fig}). These levels roughly address the questions: "Could species $i$ and $j$ interact?", "Do they interact at this site/time?" and "Do we observe the interaction?".

        \subsubsection*{Interaction uncertainty}

          First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L$ given some description of trait-matching $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$~\citep{Dom?}. In some cases the traits prohibiting an interaction are known. A potential prey may be too large, small, or well-armoured for a predator to attack, or it might be toxic or non-nutritious (e.g., large carnivores do not consume plants because they cannot digest them and typically do not consume small insects because of the large handling cost relative to the energy gained from tiny prey). Where the critical traits are known and mean that an interaction is unfeasbile, $\lambda = 0$ and there is no uncertainty about associated zeros in an interaction matrix.

          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}. Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{} and herbivores may consume animal prey when it becomes accessible~\citep{}. These examples show that we often cannot say that an interaction absolutely does not occur. Instead, an unobserved interaction may be a rare phenomenon with $\lambda>0$ and an associated zero in an interaction matrix might be false. This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016}. As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced and $\lambda$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}. Until these gaps are filled, some interaction uncertainty will remain.

          Note that interaction uncertainty does not depend upon whether species $i$ and $j$ actually co-occur. Ecologists are often interested in predicting which species are likely to interact following an introduction~\citep{} or range shift~\citep{}. In such cases, models based on trait matching can give some information about $\lambda$ while past co-occurance will, of course, not yield much insight.

        \subsubsection*{Process uncertainty} [[Maybe need to rename]]

          Assuming that an interaction is feasible (i.e., $L=1$; species traits do not prohibit an interaction if they should co-occur), an interaction still not occur at a particular place or time. This could be because the two species do not co-occur or, if they did occur, because constraints such as inclement weather or low abundance prevented the interaction. For example, a pollination interaction may not occur on a rainy day or a rare galler may not parasitize a rare plant because they do not encounter each other. 
          We can define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$. It is unlikely that $\chi$=1 except in the case of obligate specialists who always interact whenever they co-occur and always co-occur. When $\chi<1$ we cannot be sure whether an unobserved interaction did not occur and when it occurred but was not observed.

          This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology  on the topic. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species. Some of these factors can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable) or could be included in models along the line of trait-matching models (e.g., phenological matching). Expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will also help to reduce process uncertainty if resource constraints permit. In the field, however, process uncertainty is likely inevitable as long as local conditions are not constant during sampling.

         % One proposed solution to the problem of process uncertainty is to use repeated sampling of networks. For example,~\citet{Weinstein2017-wrong one?} used repeated sampling to estimate the daily probability of detecting an interaction and thereby model detection and process uncertainty.[[This apparently confused R3]] While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days. Moreover, the faster accumulation of species than interactions means that repeated sampling will tend to introduce more unobserved interactions than observed interactions unless the number of samples is very high~\citep{Poisot2012}.

@@

          Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may still fail to detect it. We may define the probability of detecting of an interaction, $D$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$. Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will approach one with increasing number of samples), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}). Some types of interactions will have higher detection uncertainty than others (e.g., pollination or predation often take place very quickly while parasitism can last for months or years). Even long-term interactions, however, can be missed, especially if species are difficult to identify or if not all individuals of a species share the interaction. Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2017}. If these infected individuals do not happen to be included in a sample, their interactions will be missed.

          To sum up, the absence of an interaction on a given day could therefore be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$]. Note that some exteral factors can affect both process and detection uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes (process uncertainty)~\citep{}. Interactions involving rare species are also less likely to be detected (detection uncertainty), unless more sampling effort is focused on rare than common species~\citep{}. Similarly, bad weather can make interactions such as pollination less likely by reducing pollinator activity~\citep{}. For those pollinators which do venture forth in poor conditions, bad weather might also reduce visibility and therefore increase detection uncertainty.

@@

        An observed interaction indicates that an interaction was feasible, occurred during sampling, and was detectable ($L = 1$, $X = 1$, and $D = 1$). An unobserved interaction could be due to any of the three sources of uncertainty ($D$, $X$, and/or $L = 0$). Only the case where $L = 0$ is an interaction that never occurs --the usual interpretation of a $0$ value in an interaction matrix. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site (Fig.~\ref{conceptual_fig}). 
        This is not possible, however, using empirical data. An empirical ecologist will instead measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?

@@

        An added complication is that increased sampling will not reduce uncertainty evenly across interactions. To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}). For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}. This can bias the set of recorded interactions towards those that are easier to observe.

        Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting should they ever co-occur. Intensive sampling is, therefore, an important step towards reducing uncertainty in ecological networks but is unlikely to be enough in most cases. To supplement repeated sampling efforts and reduce uncertainty around unobserved interactions, we suggest researchers use prior knowledge of the same or similar systems. Here, we outline a Bayesian approach to combining repeated sampling and prior knowledge in probabilistic networks. We then demonstrate how to construct such a probabilistic network using an intensively and repeatedly sampled empirical dataset. Finally, we show how a probabilistic understanding of a network allows us to establish confidence intervals around measures of network structure.

@@

        If traits governing interactions are known (e.g., body size in food webs~\citep{Gravel2013} or corolla depth in pollination networks~\citep{Graham,Weinstein}), then trait-based models may be used as a prior. Such models address interaction uncertainty directly (i.e., they estimate whether a pair of species \emph{can} interact, regardless of whether they are likely to encounter each other). To address both interaction and process uncertainty, a researcher might combine trait-based and co-occurrence models into a single prior. Such a model would reduce the uncertainty about unobserved interactions, but at the cost of adding more assumptions about the study system. This type of very detailed prior is therefore most appropriate in very well-understood systems where a great deal of expert knowledge can be applied.

@@

  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, leading to pervasive under-estimation of interactions in published networks. Even in the most extensive data set that we could find, there was very little empirical data for each species pair. Most pairs of species were not observed co-occurring even once, less than 10\% of species pairs were observed interacting, and no pairs were observed to co-occur frequently enough to conclude that their probability of interacting was below 0.01. This suggests that limited sampling is a major source of uncertainty in empirical networks. This dataset also illustrates the problem of process uncertainty - pairs of species which were observed interacting did not interact in all of the samples in which they co-occurred. Increasing sampling is therefore likely to add more zeros than ones to an interaction network.

@@

  Based on the framework described above, we can now offer some recommendations for improved descriptions of ecological interactions. First, sample sizes should be as large as possible in order to reduce detection uncertainty. Second, researchers should acknowledge the varying levels of confidence surrounding interactions between species pairs. In the absence of strong prior information a very high level of sampling (i.e., 30-50 observations in our example) is needed \emph{for each species pair}. This is not likely to be possible for most studies. including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable. Where there are strong prior expectations about pairs of species that will not interact, these should be explicitly stated so that readers know which zeros in an interaction matrix are based on observed data and which are based primarily upon expert knowledge. Third, the uncertainty around interactions should be incorporated in calculations of network properties. Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates. This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties. This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions. To facilitate the practical application of these recommendations, we provide all code used in this paper in the supplementary material.

@@

\begin{figure}[h!]
\caption{\textbf{Why isn't sampling the solution?}
While sufficient sampling is a vital part of any scientific study, we do not think that an exhortation to "sample more" is the appropriate solution to analysing uncertain interactions. There are four main reasons for this: \\
\textbf{1)} First, and most importantly, we assume that the majority of researchers are aware that insufficient sampling leads to shoddy data and are sampling as intensively and extensively as their time and budget allow. The development and decreasing price of novel methods such as DNA barcoding and remote sensing can help field researchers to do more with less, but it remains to be seen whether these improvements will be enough to fully-describe large study systems. \\
\textbf{2)} High sampling effort with a constant methodology will reliably describe some interactions but not others. For example, many insect species are difficult to distinguish except by molecular methods. Non-descructive sampling (e.g., by observing insect flower-visitors) will not allow researchers to separate these cryptic species~\citep{}. Increasing the number of person-hours spent in the field will not change this situation, although of course it will allow more accurate estimations of interaction probabilities for species which \emph{can} be distinguished. Adding another type of sampling (e.g., molecular methods) would reduce the set of interactions which cannot be detected/distinguished, but it will also increase the time, resources, and expertise required to complete the study. \\
\textbf{3)} High sampling effort in a narrow spatiotemporal window will reliably describe some interactions but not others. Species abundances vary between sites and over time, and some interactions may not occur if one or both partners is rare. In addition, some interactions only occur in brief temporal windows (e.g., flowers of Arctic plants may only open for a few days~\citep{}) or when mediated by other species (e.g., consumption of some shellfish by fish only occurs when the shellfish are heavily parasitised and cannot burrow~\citep{}). Expanding sampling to cover broader ranges of space and time will expand the set of interactions that are observed, but again will increase the time and resources needed. \\
\textbf{4)}{} Observations of rare species add disproportionately more "zeros" than ones to an interaction matrix. Rare species may appear to be specialists purely because of their rarity~\citep{}. If increasing sampling effort adds many rare species to a network, but each species is observed only one or a few times, it is likely that only a fraction of the rare species' interactions will be included. Note that we should not avoid sampling rare species! It is better to identify species about which we know little as targets for future study than to ignore these species. Nevertheless, sampling which is sufficiently high to identify most species at a site but not most interactions for rare species will underestimate the number of interactions and skew the distribution of interactions to rare species. Targeted sampling of rare species would reduce this problem, but again either increase the cost of a study or take away resources from sampling more abundant species. \\
Increased or targeted sampling could improve (and, given enough resources, perhaps solve) any one of the above problems. As each places demands on the same limited resource pool, however, it is extremely unlikely that researchers will be able to sample their way out of uncertainty about interactions. To illustrate the scale of sampling needed, we can consider the observation of an interaction as a Bernoulli trial. The number of successes ($k$ observed interaction) over ($n$ observed co-occurrances) trials will follow a binomial distribution (see~\emph{Appendix S2} for a full description of the mathematical framework). In this framework, the maximum likelihood estimate (MLE) for $\lambda$ is:

>>>>

    First and foremost, ecological communities are known to be stochastic~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilites and hence in interactions~\citep{Vazquez2005,Poisot2015,Graham2018}. Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013,Graham2018}. Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012,Emer2018}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}, throughout life cycles~\citep{Preston2014,Clegg2018}, and with environmental conditions~\citep{Poisot2015}.

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007,Jordano2016}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeeus2013,Poisot2016}. Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}. These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}. Such networks provide an important ''reality check'' by allowing us to compare the observed network to what would be expected under a particular set of assumptions~\citep{Bartomeus2013,Weinstein??}. They allow us to estimate the numbers of interactions which have not been observed~\citep{Jordano2016,Weinstein2017} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.

@@

      We start from the perspective of a community ecologist faced with the task of describing a previously unknown interaction network. This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.  Importantly, the information sought is conveyed by both the presence and \emph{absence} of links. Presences and absences are not, however, equally certain. An observed link definitely occurred, but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}. In terms of the ones and zeros in a binary interaction matrix, we know that the ones are true but we cannot be sure that the zeros reflect interactions which actually do not occur. The detection of any interaction is a stochastic process. As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty that roughly address the questions: "Could species $i$ and $j$ interact?", "Do they interact?" and "Do we observe the interaction?" (Fig.~\ref{conceptual_fig}).

        \subsubsection*{Could the species interact under ideal conditions?}

          First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L$ given some description of trait-matching $\mathbf{T}$ as $P(L|\mathbf{T}) = \lambda$~\citep{Gravel2013,others}. 
          In some cases the traits prohibiting an interaction are known, and there will be little uncertainty about $\lambda$.
          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}. Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017} and herbivores may consume animal prey when it becomes accessible~\citep{}. These examples show that we often cannot say that an interaction absolutely does not occur. Instead, an unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false. This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016,Jordano2016}. As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced~\citep{Jordano2016} and $\lambda$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}. Until these gaps are filled, some uncertainty will remain about whether some species pairs could interact.

        \subsubsection*{Did the species interact during sampling?}

          Assuming that an interaction is feasible (i.e., $L=1$;), an interaction may still not occur at a particular place or time~\citep{Graham2018}. This could be because the two species do not co-occur or, if they did occur, because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018} or because a more preferred interaction partnre was available~\citep{Weinstein2017}. For example, a rare galler may not parasitize a rare plant because they do not encounter each other. 
          We can define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$. It is unlikely that $\chi=1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur. When $\chi<1$ we cannot be sure whether an unobserved interaction did not occur and when it occurred but was not observed.

          This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology  on the topic. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species. Some of these factors can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable) or could be included in models along the line of trait-matching models (e.g., phenological matching). Expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will also help to reduce uncertainty if resource constraints permit. As long as researchers wish to sample empirical networks subject to changing conditions, however, it is not likely that they will be able to eliminate all uncertainty about whether or not pairs of species will interact during a given sampling period.

         % One proposed solution to the problem of process uncertainty is to use repeated sampling of networks. For example,~\citet{Weinstein2017-wrong one?} used repeated sampling to estimate the daily probability of detecting an interaction and thereby attempted to separate detection and process uncertainty.[[This apparently confused R3]] While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), which would require multi-year sampling efforts, or very rare interactions which would require extremely high sampling effort to detect. Moreover, the faster accumulation of species than interactions means that repeated sampling will tend to introduce more unobserved interactions than observed interactions unless the number of samples is high enough to ensure that all species present have been observed~\citep{Poisot2012,Jordano2016}.

          \textbf{Forbidden links}

            Both of the above sources of uncertainty (i.e., whether species would be able to interact given their traits and whether they are able to interact at a particular place and time) are addressed in the concept of "forbidden links"~\citep{Jordano2016}. In this framework, all links which are prevented by spatio-temporal uncoupling~\citep{Jordano1987}, physiological constraints~\citep{Jordano1987,More2012}, etc. are considered "structural zeros" that cannot be observed~\citep{Jordano2016}. We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology. In such cases, links which are forbidden due to physiological constraints remain forbidden but links previously forbidden due to spatio-temporal mismatch could potentially occur.

@@

          Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may still fail to detect it~\citep{Jordano2016,Weinstein2017}. We may define the probability of detecting of an interaction, $D$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$. Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort (e.g., combining plant-focused and animal-focused sampling when assembling pollination networks~\citet{Jordano2016}), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}). Some types of interactions will have higher detection uncertainty than others (e.g., pollination or predation often take place very quickly while parasitism can last for months or years). Even long-term interactions, however, can be missed, especially if species are difficult to identify or if not all individuals of a species share the interaction. Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2017}. If these infected individuals do not happen to be included in a sample, their interactions will be missed.

      To sum up, the absence of an interaction on a given day could  be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$]. Note that some exteral factors can affect more than one level of uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes~\citep{}. Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Jordano2016}. Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction. Similarly, bad weather can make interactions such as pollination less likely by reducing pollinator activity~\citep{}. For those pollinators which do venture forth in poor conditions, bad weather might also  increase detection uncertainty through reduced visibility or if pollinators make shorter trips. The "forbidden links" of~\citet{Jordano2016} can also occur due to process or interaction uncertainty in our framework.

@@

        An observed interaction indicates that an interaction was feasible, occurred during sampling, and was detectable ($L = 1$, $X = 1$, and $D = 1$). An unobserved interaction could be due to any of the three sources of uncertainty ($D$, $X$, and/or $L = 0$) and it is not usually possible to identify the source in empirical data. Only the case where $L = 0$ is an interaction that never occurs --the usual interpretation of a $0$ value in an interaction matrix. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site (Fig.~\ref{conceptual_fig}). An empirical ecologist will instead measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?

@@

        An added complication is that increased sampling will not reduce uncertainty evenly across interactions. To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}). For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}. This can bias the set of recorded interactions towards those that are easier to observe~\citep{Jordano2016}.

        Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting should they ever co-occur. Intensive sampling is, therefore, an important step towards reducing uncertainty in ecological networks but is unlikely to be enough in most cases. 
        Indeed, despite substantial improvements in recent decades, most available interaction networks are still undersampled and, moreover, are only subsets of larger communities~\citep{Jordano2016}.
        To supplement repeated sampling efforts and reduce uncertainty around unobserved interactions, we suggest researchers use prior knowledge of the same or similar systems. Here, we outline a Bayesian approach to combining repeated sampling and prior knowledge in probabilistic networks. We then demonstrate how to construct such a probabilistic network using an intensively and repeatedly sampled empirical dataset. Finally, we show how a probabilistic understanding of a network allows us to establish confidence intervals around measures of network structure.

@@

        If traits governing interactions are known (e.g., body size in food webs~\citep{Gravel2013} or corolla depth in pollination networks~\citep{Weinstein2017,Graham}), then trait-based models may be used as a prior. Such models address interaction uncertainty directly (i.e., they estimate whether a pair of species \emph{can} interact, regardless of whether they are likely to encounter each other). To address both interaction and process uncertainty, a researcher might combine trait-based and co-occurrence models into a single prior. Such a model would reduce the uncertainty about unobserved interactions, but at the cost of adding more assumptions about the study system. This type of very detailed prior is therefore most appropriate in very well-understood systems where a great deal of expert knowledge can be applied.

        An informed prior could be based on one or a few traits, as those described above, or it could incorporate a great deal of information about co-occurrence and encounter probabilities, forbidden links, etc.~\citep{Jordano2016}. Importantly, the complexity of a prior model depends both on the information available and on the question of interest. If researchers wish to test for an effect of body mass ratios on interaction probabilities, for example, they should not include body mass in their prior. Including a trait in a prior means assuming that trait has an effect on which interactions we detect and it is therefore inappropriate to test for such an effect in the same study.

        The relevant traits and degree of trait-matching between interaction partners is likely to vary between systems~\citep{Gravel2013,Weinstein2017}. We therefore urge caution when using a model developed for one system as the prior for another.

@@

  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, leading to pervasive under-estimation of interactions in published networks~\citep{Jordano2016}. Even in the most extensive data set that we could find, there was very little empirical data for each species pair. Most pairs of species were not observed co-occurring even once, less than 10\% of species pairs were observed interacting, and no pairs were observed to co-occur frequently enough to conclude that their probability of interacting was below 0.01. This suggests that limited sampling is a major source of uncertainty in empirical networks. This dataset also illustrates the problem of process uncertainty - pairs of species which were observed interacting did not interact in all of the samples in which they co-occurred. Increasing sampling is therefore likely to add more zeros than ones to an interaction network.

  Detectability estimated at 23.3\% in~\citet{Weinstein2017}

@@

  Based on the framework described above, we can now offer some recommendations for improved descriptions of ecological interactions. Observing all interactions in a network is likely impossible~\citep{Jordano2016}, but researchers can take steps to address the uncertainty this implies. First, sample sizes should be as large as possible in order to reduce detection uncertainty. Second, researchers should acknowledge the varying levels of confidence surrounding interactions between species pairs. Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable. Where there are strong prior expectations about pairs of species that will not interact, these should be explicitly stated so that readers know which zeros in an interaction matrix are based on observed data and which are based primarily upon expert knowledge. Third, the uncertainty around interactions should be incorporated in calculations of network properties. Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates. This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties. This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions. To facilitate the practical application of these recommendations, we provide all code used in this paper in the supplementary material.

@@

\begin{figure}[h!]
\caption{\textbf{Why isn't sampling the solution?}
While sufficient sampling is a vital part of any scientific study, we do not think that an exhortation to "sample more" is the appropriate solution to analysing uncertain interactions. There are four main reasons for this: \\
\textbf{1)} First, and most importantly, we assume that the majority of researchers are aware that insufficient sampling leads to shoddy data and are sampling as intensively and extensively as their time and budget allow. The development and decreasing price of novel methods such as DNA barcoding and remote sensing can help field researchers to do more with less, but it remains to be seen whether these improvements will be enough to fully-describe large study systems. In the absence of new break-through sampling techniques, logistical limitations mean that allocating sampling effort is a zero-sum game. That is, allocating more sampling to reduce one source of uncertainty will remove sampling effort that could reduce another source of uncertainty.\\
\textbf{2)} High sampling effort with a constant methodology will reliably describe some interactions but not others. For example, many insect species are difficult to distinguish except by molecular methods. Non-descructive sampling (e.g., by observing insect flower-visitors) will not allow researchers to separate these cryptic species~\citep{}. Increasing the number of person-hours spent in the field will not change this situation, although of course it will allow more accurate estimations of interaction probabilities for species which \emph{can} be distinguished. Adding another type of sampling (e.g., molecular methods) would reduce the set of interactions which cannot be detected/distinguished, but it will also increase the time, resources, and expertise required to complete the study. \\
\textbf{3)} High sampling effort in a narrow spatiotemporal window will reliably describe some interactions but not others. Species abundances vary between sites and over time, and some interactions may not occur if one or both partners is rare. In addition, some interactions only occur in brief temporal windows (e.g., flowers of Arctic plants may only open for a few days~\citep{}) or when mediated by other species (e.g., consumption of some shellfish by fish only occurs when the shellfish are heavily parasitised and cannot burrow~\citep{}). Expanding sampling to cover broader ranges of space and time will expand the set of interactions that are observed, but again will increase the time and resources needed. \\
\textbf{4)}{} Observations of rare species add disproportionately more "zeros" than ones to an interaction matrix. Rare species may appear to be specialists purely because of their rarity~\citep{}. If increasing sampling effort adds many rare species to a network, but each species is observed only one or a few times, it is likely that only a fraction of the rare species' interactions will be included. Note that we should not avoid sampling rare species! It is better to identify species about which we know little as targets for future study than to ignore these species. Nevertheless, sampling which is sufficiently high to identify most species at a site but not most interactions for rare species will underestimate the number of interactions and skew the distribution of interactions to rare species. Targeted sampling of rare species would reduce this problem, but again either increase the cost of a study or take away resources from sampling more abundant species. \\
Increased or targeted sampling could improve (and, given enough resources, perhaps solve) any one of the above problems. As each places demands on the same limited resource pool, however, it is extremely unlikely that researchers will be able to sample their way out of uncertainty about interactions. To illustrate the scale of sampling needed, we can consider the observation of an interaction as a Bernoulli trial. The number of successes ($k$ observed interaction) over ($n$ observed co-occurrances) trials will follow a binomial distribution (see~\emph{Appendix S2} for a full description of the mathematical framework). In this framework, the maximum likelihood estimate (MLE) for $\lambda$ is:
